Implementing Equational Constraints\\ in a Functional Language

### 2011-07-01 papers/wlp2011/paper.tex
added more benchmarks

Unlike the Curry implementations PAKCS and MCC our approach does
not manipulate a global state to unify a logic variable. Nevertheless,
our benchmarks show that it can compete or even outperform these 
implementations.
The programs used for the benchmarks are primarily the same as in \cite{AntoyHanus05LOPSTR}.

@@

\begin{tabular}{|l|c|c|c|}
\hline
Expression: & KiCS2 & PAKCS & MCC \\
\code{last (map (inc 0) [1..100000])} & &  & \\
\code{simplify}                       &&&\\
\code{varsInExp} & &  &\\
\code{toPeano 5000 == halfS (toPeano 10000)} & &  &\\
\hline
\end{tabular}

All of our examples can also be defined with function patterns, i.e.,
the lazy equality operator \code{=:<=} is used. The sole other
Curry system featuring function patterns is PAKCS:

\begin{tabular}{|l|c|c|c|}
\hline
Expression: & KiCS2 & PAKCS \\
\code{last (map (inc 0) [1..100000])} & &  & \\
\code{simplify}                       &&&\\
\code{varsInExp} & &  &\\
\code{toPeano 5000 == halfS (toPeano 10000)} & &  &\\
\hline
\end{tabular}

@@

\begin{tabular}{|l|c|c|c|}
\hline
Expression: &\code{==} & \code{=:=} & \code{=:<=}\\
\hline 
\code{last (map (inc 0) [1..100000])} & stack overflow & 0.45 & 0.13\\
\code{simplify}                       &10.34&10.33&7.27\\
\code{varsInExp} & 0.49& 84.92 & 0.09\\
\code{toPeano 5000 == halfS (toPeano 10000)} & 23.3 & 1.81 & no Fun Pat\\
\hline
\end{tabular}

>>>>

Unlike the Curry implementations PAKCS and MCC our approach does
not manipulate a global state to unify a logic variable. Nevertheless,
our benchmarks show that it can in most cases
compete or even outperform these implementations.
The programs used for the benchmarks are primarily the same as in \cite{AntoyHanus05LOPSTR}.

@@

\begin{tabular}{|l|c|c|c|}
\hline
Expression: & KiCS2 & PAKCS & MCC \\
\code{last (map (inc 0) [1..100000])} &0.52 & 4.27&0.15 \\
\code{grep} & 0.13& 2.83& 0.15\\
\code{simplify} &10.33&0.15&0.01\\
\code{varsInExp} & 86.27 & 0.35  & 0.03\\
\code{fromPeano (half (toPeano 10000))} & &  & \\
\code{palindrom} & 13.45 &32.82 & 1.04\\
\code{horseman} & & &\\
\hline
\end{tabular}

Some of our examples can also be defined with function patterns, i.e.,
the lazy equality operator \code{=:<=} is used. The sole other
Curry system featuring function patterns is PAKCS:

\begin{tabular}{|l|c|c|c|}
\hline
Expression: & KiCS2 & PAKCS \\
\code{last (map (inc 0) [1..100000])} & 0.20& 3.93\\
\code{simplify}  &7.09&0.26&\\
\code{varsInExp} & 0.14 & 0.69\\
\code{fromPeano (half (toPeano 10000))} & &  \\
\code{palindrom} & 17.55 & $\infty$\\
\code{horseman} & & \\
\hline
\end{tabular}

@@

\begin{tabular}{|l|c|c|c|}
\hline
Expression: &\code{==} & \code{=:=} & \code{=:<=}\\
\hline 
\code{last (map (inc 0) [1..100000])} & 118.33 & 0.52 & 1.40 \\
\code{grep} & 0.94 & 0.13 &\\
\code{simplify} & 9.18& 10.33 & 7.09\\
\code{varsInExp} & 0.50& 86.27 & 0.14\\
\code{fromPeano (half (toPeano 10000))} &  &  & \\
\code{palindrom} & 31.12&13.45 & 17.55\\
\code{horseman} & & & \\
\hline
\end{tabular}
